\documentclass[11pt]{article}
\usepackage[left=1cm, top=1cm, right=1cm, bottom=1cm]{geometry} % margins
\setlength{\parindent}{0pt} % no indent
\pagenumbering{gobble} % no page number

\usepackage{enumitem} % lists
\usepackage{hyperref} % hyperlinks
\hypersetup{ pdfborder = {0 0 0} } % no link border

\usepackage[utf8]{inputenc} % UTF-8 encoding
\usepackage[T1]{fontenc} % font encoding

\usepackage{graphicx} % images
\usepackage{fontawesome5} % icons
\usepackage[dvipsnames]{xcolor} % color


\begin{document}

% -------------------------------------------------- Header --- %
\begin{center}
    {\Large \textbf{Pupipat Singkhorn}} \\
    \faPhone* 082-642-9767 \textbullet\ pupipat.sk@gmail.com \textbullet\ Itsaraphap 31 Road, Bangkok
    \\
    \href{www.linkedin.com/in/pupipatsk}{\faLinkedin\ LinkedIn.com/pupipatsk}
    \textbullet\ \href{https://github.com/pupipatsk}{\faGithub\ Github.com/pupipatsk}
    \textbullet\ \href{https://pupipatsk.github.io/resume/}{\faGlobe\ https://pupipatsk.github.io/resume/}
\end{center}
% -------------------------------------------------- Education --- %
\textbf{EDUCATION}
\vspace{5pt}
{\color{NavyBlue}\hrule}
\vspace{6pt}

\textbf{Chulalongkorn University} \hfill 2022 - Present

\hspace*{7pt} Bachelor of Engineering - Computer Engineering Major.\\
\hspace*{7pt} Relevant Coursework: Pattern Recognition, Algorithm Design, Data Structures, Database Systems

\vspace{2pt}

\textbf{Triam Udom Suksa School} \hfill 2019 - 2022\\
\textit{Science-Mathematics Major. GPAX: 3.85}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item \textit{Thailand Physics Olympiad (TPhO)} - 19th TPhO: Bronze Medal, 18th TPhO: Participated
    \item \textit{Triam Udom Photo Club (Staff and Member)} - Captured photos at various school events.
\end{itemize}

\vspace{6pt}
% -------------------------------------------------- Work Experience --- %
\textbf{WORK EXPERIENCE}
\vspace{5pt}
{\color{NavyBlue}\hrule}
\vspace{6pt}

\textbf{Data Scientist Intern} - Kiatnakin Phatra Bank \hfill June 2024 - July 2024

\begin{itemize}[topsep=0pt, parsep=0pt]
    \item \textit{Used Car Price Forecasting}
    {\fontsize{10pt}{11pt}\selectfont
    \begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
        \item Developed an ensemble machine learning model to predict used car prices, aiding informed automotive loan decisions.
        \item Conducted comprehensive data collection and cleaning from a real-world business dataset, integrating macro-, and micro-economic factors.
        \item Utilized time-series cluster analysis and Bayesian optimization techniques.
    \end{itemize}
    }
    \item \textit{Loss On Sale Forecasting}
    {\fontsize{10pt}{11pt}\selectfont
    \begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
        \item Created a model to predict loss on sale for Non-Performing Loans (NPLs), reducing uncertainty in credit cost estimation.
        \item Utilized credit score, personal data, and credit risk factors to improve model accuracy.
        \item Applied coarse classing, binning-, and memory-optimization techniques to enhance model performance and efficiency.
    \end{itemize}
    }
\end{itemize}

\textbf{Freelance}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item \textit{Physics} \& \textit{Mathematics Tutor} - Provided lessons for Physics Olympiad camp, university admissions preparation.
    \item \textit{Photographer} - Portfolio: \href{https://www.instagram.com/pupick.sk/}{instagram.com/pupick.sk} - Captured photos at events and private photo sessions.
\end{itemize}

\vspace{6pt}
% -------------------------------------------------- Extracurricular Activities & Achievements --- %
\textbf{EXTRACURRICULAR ACTIVITIES \& ACHIEVEMENT}
\vspace{5pt}
{\color{NavyBlue}\hrule}
\vspace{6pt}

\textbf{Aihack Thailand 2023 - Ai Hackathon} \hfill December 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Created a credit risk model using a machine learning approach to forecast individuals who are likely to default.
    \item Performed data analysis, data pre-processing, and feature engineering using linear and tree-based models.
    \item Awarded 1st Prize Winner \& AUC Prize Winner.
\end{itemize}

\vspace{3pt}

\textbf{Stock Return Forecasting with Portfolio Optimization Project} \hfill April-May 2024
% \\ {\footnotesize Pattern Recognition 2024 Class Final Project}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed an Alpha Factor Model for stock return forecasting using Classical ML and LSTM networks.
    \item Designed and backtested trading strategies, integrating portfolio optimization for improved performance.
    % \item Implemented Portfolio Optimization techniques within trading strategies.
\end{itemize}

\vspace{3pt}

\textbf{SAS xCBS Hackathon Season 4} \hfill October 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Applied predictive modeling to optimize donor outreach in a direct-contact fundraising campaign.
    \item Built a 2-stage ensemble model with a pipeline for precise predictions and improved targeting.
    \item Achieved 4th place by strategically balancing donation forecasts with contact costs.
\end{itemize}

\vspace{3pt}

\textbf{Participated in Business Case Competition} \hfill 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item \textit{Hult Prize at Chulalongkorn} - Developed a social enterprise Idea aligned with the UN SDGs.
    \item \textit{Chulalongkorn Case Discovery x Ascend Money} - Formulated a strategy for financial services application.
\end{itemize}

\vspace{3pt}

\textbf{Certifications}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item \textit{Machine Learning Specialization} - Issued by: DeepLearning.AI, Stanford University \hfill August 2024
    \item \textit{Google Data Analytics Professional} - Issued by: Google \hfill July 2023
    \item \textit{Financial Engineering and Artificial Intelligence in Python} - Issued by: Udemy \hfill August 2024
\end{itemize}

% \vspace{6pt}

% \textbf{Final round in Space Youth Challenge by NARIT} \hfill December 2021\\
% \hspace*{7pt} Presented ideas on meteor prevention at the National Science and Technology Fair 2021.

% \vspace{6pt}

% \textbf{Participated in The 2nd Kibo Robot Programming Challenge by NSTDA x JAXA} \hfill July 2021\\
% \hspace*{7pt} Programmed a robot to move in a specified direction while on the International Space Station (ISS).

\vspace{6pt}
% -------------------------------------------------- Miscellaneous --- %
\textbf{MISCELLANEOUS}
\vspace{5pt}
{\color{NavyBlue}\hrule}
\vspace{6pt}

\textbf{Technical Skills}\\
\hspace*{7pt} Programming Language: Python, SQL, C++, C, HTML, CSS, LaTex, Markdown\\
\hspace*{7pt} Programming Libraries: PyTorch, Scikit-learn, Pandas, NumPy, Matplotlib, Plotly\\
\hspace*{7pt} Applications: Excel, Power BI, Tableau, Git, GitHub

\textbf{Language:} Thai (Native), English

\textbf{Interests:} Business, Economics, Politics, Books, History, Philosophy


\end{document}
